|

### 2022-12-13 r-report/Paper.Rmd
final

```{r,fig.cap="Relative Emissions of the Top- 5 Polluters"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR_L = 1970
YEAR_U = 2020
GAS = "GHG"
COUNTRY = "China"

@@

```{r,fig.cap="Total Emissions, China by Sector - 1970-2019"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR_L = 1970
YEAR_U = 2019
GAS = "GHG"
COUNTRY = "China"

@@

```{r,fig.cap="Kaya Identity China - 2000 - 2019"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR_L = 2000
YEAR_U = 2019
GAS = "GHG"

@@

```{r,fig.cap="Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR_L = 2000
YEAR_U = 201
COUNTRY = "China"
GAS = "GHG"

@@

```{r,fig.cap="Kaya Identities - 2000 - 2019| China vs. Income Levels"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR_L = 2000
YEAR_U = 2019
GAS = "GHG"

@@

In this part, sector trends of different groups of countries will be considered using the same two categories of country groups as before. We take into account five sectors: energy, industry, transport, AFOLU (which in the EDGAR database only includes agricultural emissions), and buildings. China’s relative GHG emissions by sector are presented in a stacked bar plot in Figure 3.3 & 3.4 Most of China’s emissions in 2019 came from the energy and industry sector with 44% and 38% respectively. Only smaller shares are attributable to transport (6%), buildings (5%) and AFOLU (6%).

@@

```{r,fig.cap="Relative sector Emissions-2019| China vs. Developed vs. Developing"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR = 1950
GAS = "GHG"
COUNTRY = "China"

@@

As before, to get a more granular view on the split of emissions by sector, the World Bank’s classification will be consulted (Figure 3.5).

@@

```{r,fig.cap="Relative sector Emissions - 2019| China vs. Income Levels"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR = 1950
GAS = "GHG"
COUNTRY = "China"

@@

As the stacked bar plot can only provide a snapshot in time and relative emissions only tell a limited story, we will in a next step compare China’s per capita emissions by sector over time from 1970 to 2019 to those of our four income determined country groups (Figure 3.6).

@@

```{r,fig.cap="1970-2019| China vs. Income Levels"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)

@@

The resulting sectoral emissions pathways for each country/region are depicted in figure xx. The resulting cumulative emissions forecasts for the three countries/blocks are shown in figure xx. Accordingly, China will pass the EU-27 in cumulative GHG emissions in 2027 and is projected to pass the U.S. in 2032 . Afterwards it will be the largest cumulative emitter.

These projections hold even when modelling each sector according to the Chinese NDC (assuming peak years of 2030 and zero emissions by 2060). In the NDC-scenario China will surpass the EU and US respectively in the same years as modeled in our main scenarios, but at different emission levels – 452.4 GtCO2eq (main scenario)  451.8 GtCO2eq (NDC-scenario). When projecting only  CO2 emission developments1 China will surpass the EU in 2031 and the US in 2038 according to both scenarios.

@@

```{r,fig.cap="Figure 9"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)

@@

First, we consider China’s responsibility based on absolute emissions in the year 2019 (Figure X). In the ranking, China ranks on first place with absolute emissions of 14,219.37 Mt CO2 eq. This is more than double of the U.S. emissions (6,266.8 Mt CO2 eq) and also close to the emissions of all other countries that do not belong to the group of the top 10 emitters combined (14,075.12 Mt CO2 eq). Together with the U.S., India and Russia, China makes up for 50% of global emissions, but these four countries do not produce half of the global GDP, nor do they represent half of the world’s population. This highlights that the responsibility of these four countries to drastically reduce emissions is high. Considering that China is producing more than double the emissions of the U.S., China has by far the highest responsibility to mitigate climate change from a current absolute emissions perspective.

```{r,fig.cap="Figure 10: Absolute GHG Emission - 2019 | Top Emittters, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

Next, we consider emissions per capita (Figure x). This is important as China is the country with the biggest population worldwide of approx. 1.4 billion people [@WorldBank2022c]. Looking at this ranking, it is important to consider that the top emitters according to per capita emissions are relatively small countries with low absolute emissions but also small populations. Thus, when it comes to reducing absolute emissions and fighting climate change, they can only play a minor role. China interestingly ranks on place 43 with roughly 10t CO2 eq / capita, before EU-27 but behind the U.S. (Ranking: 17). According to this equity metric, China’s fair share to mitigate climate change from this perspective should be located between the share of these two countries/groups of countries.

```{r,fig.cap="Figure 11: Per Capita Emissions- 2019 | Top Emittters, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

Considering GDP and GDP per capita refers to the capacity of acting on climate change, following the assumption that richer countries have more resources available to fight climate change. As Figure XX shows, China had the highest GDP of all countries in 2019, with USD 22.49 trillion. Based on this, China would theoretically have to make the greatest conribution to reduce emissions. Absolute GDP, however, is limited in telling us about a country's actual capacity because it ignores population size. Therefore, considering GDP per capita might be more worthwhile. Here China only ranks 81st place in the world. Therefore, China’s responsibility is relatively low from the GDP per capita perspective. In comparison, the U.S. rank on place 11. Countries that are in the top 10 emitters are often relatively small countries deriving their wealth from natural resources. Hence, they have a high responsibility to mitigate climate change as they have the ability to pay for climate change mitigation measures. However, their absolute emissions are relatively small and thus an ambitious reduction might not make a huge difference for achieving climate targets. Thus, one should consider that these countries should specifically contribute by providing financial aid to mitigate emissions elsewhere.

```{r,fig.cap="Figure 12: Absolute GDP p - 2019 | Highes GDP Countries, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

```{r,fig.cap="Figure 13: GDP per Capita - 2019 | Highes GDP Countries, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

>>>>

```{r init}
```
```{r,fig.cap="Relative Emissions of the Top-5 Polluters"}
YEAR_L = 1970
YEAR_U = 2020
GAS = "GHG"
COUNTRY = "China"

@@

```{r init}
```
```{r,fig.cap="Total Emissions, China, by Sector, 1970-2019"}
YEAR_L = 1970
YEAR_U = 2019
GAS = "GHG"
COUNTRY = "China"

@@

```{r init}
```
```{r,fig.cap="Kaya Identity, China, 2000-2019"}
YEAR_L = 2000
YEAR_U = 2019
GAS = "GHG"

@@

```{r init}
```
```{r,fig.cap="Kaya Identities, 2000-2019, China vs. Developed/Developing according to AR_6 Classification"}
YEAR_L = 2000
YEAR_U = 201
COUNTRY = "China"
GAS = "GHG"

@@

```{r init}
```
```{r,fig.cap="Kaya Identities, 2000-2019, China vs. Developed and Developing according to AR_6 Classification"}
YEAR_L = 2000
YEAR_U = 2019
GAS = "GHG"

@@

In this part, sector trends of different groups of countries will be considered using the same two categories of country groups as before. We take into account five sectors: energy, industry, transport, AFOLU (which in the EDGAR database only includes agricultural emissions), and buildings. China’s relative GHG emissions by sector are presented in a stacked bar plot in Figure 3.3 & 3.4. Most of China’s emissions in 2019 came from the energy and industry sector with 44% and 38% respectively. Only smaller shares are attributable to transport (6%), buildings (5%) and AFOLU (6%).

@@

```{r init}
```
```{r,fig.cap="Relative Sector Emissions, 2019, China vs. Developed/Developing according to AR_6 Classification"}
YEAR = 2019
GAS = "GHG"
COUNTRY = "China"

@@

As before, to get a more granular view on the split of emissions by sector, the World Bank’s classification will be consulted (Figure 3.4).

@@

```{r init}
```
```{r,fig.cap="Relative Sector Emissions, 2019, China vs. Countries classified by Income Levels"}
YEAR = 2019
GAS = "GHG"
COUNTRY = "China"

@@

As the stacked bar plot can only provide a snapshot in time and relative emissions only tell a limited story, we will in a next step compare China’s per capita emissions by sector over time from 1970 to 2019 to those of our four income determined country groups (Figure 3.5).

@@

```{r init}
```
```{r,fig.cap="Per Capita Emissions, by Sector, 1970-2019, China vs. Countries classified by Income Levels"}
YEAR_L = 1970
YEAR_U = 2019
GAS = "GHG"
COUNTRY = "China"

source("r-analysis/data_sector_incomelevel.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_facet_incomelevels_sectors_emissions.R", local = TRUE, print.eval = TRUE)

@@

The resulting sectoral emissions pathways for each country/region are depicted in Figure 3.6, with change rates being displayed in Figure 3.7. The resulting cumulative emissions forecasts for the three countries/blocks are shown in Figure 3.8. Accordingly, China will pass the EU-27 in cumulative GHG emissions in 2027 and is projected to pass the U.S. in 2032. Afterwards it will be the largest cumulative emitter.

These projections hold even when modelling each sector according to the Chinese NDC (assuming peak years of 2030 and zero emissions by 2060, see Figure 3.9 for comparison). In the NDC-scenario China will surpass the EU and US respectively in the same years as modeled in our main scenarios, but at different emission levels – 452.4 GtCO2eq (main scenario)  451.8 GtCO2eq (NDC-scenario). When projecting only  CO2 emission developments1 China will surpass the EU in 2031 and the US in 2038 according to both scenarios.

@@

```{r init}
```
```{r,fig.cap="GHG Emissions Forecast, China vs. EU vs. US"}
YEAR_L = 1970
YEAR_U = 2019
FYEAR_L = c(2025,2030,2030,2035,2040)
FYEAR_U = c(2060,2060,2055,2065,2065)
FYEAR_US = 2050
FYEAR_EU = 2050
GAS = "GHG"

source("r-analysis/forecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_forecast.R", local = TRUE, print.eval = TRUE)

```{r,fig.cap="GHG Emissions Forecast, China vs. EU vs. US"}
source("r-plots/plot_forecast_delta.R", local = TRUE, print.eval = TRUE)

```{r init}
```
```{r,fig.cap="Projected Cumulative Emissions, China, NDC Scenario"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_cumulative_china_2040.R", local = TRUE, print.eval = TRUE)

```{r,fig.cap="Projected Cumulative Emissions, China, Main Scenario"}
source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)

@@

First, we consider China’s responsibility based on absolute emissions in the year 2019 (Figure 3.10). In the ranking, China ranks on first place with absolute emissions of 14,219.37 Mt CO2 eq. This is more than double of the U.S. emissions (6,266.8 Mt CO2 eq) and also close to the emissions of all other countries that do not belong to the group of the top 10 emitters combined (14,075.12 Mt CO2 eq). Together with the U.S., India and Russia, China makes up for 50% of global emissions, but these four countries do not produce half of the global GDP, nor do they represent half of the world’s population. This highlights that the responsibility of these four countries to drastically reduce emissions is high. Considering that China is producing more than double the emissions of the U.S., China has by far the highest responsibility to mitigate climate change from a current absolute emissions perspective.

```{r init}
```
```{r,fig.cap="Absolute GHG Emissions, 2019, Top Emittters, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

Next, we consider emissions per capita (Figure 3.11). This is important as China is the country with the biggest population worldwide of approx. 1.4 billion people [@WorldBank2022c]. Looking at this ranking, it is important to consider that the top emitters according to per capita emissions are relatively small countries with low absolute emissions but also small populations. Thus, when it comes to reducing absolute emissions and fighting climate change, they can only play a minor role. China interestingly ranks on place 43 with roughly 10t CO2 eq / capita, before EU-27 but behind the U.S. (Ranking: 17). According to this equity metric, China’s fair share to mitigate climate change from this perspective should be located between the share of these two countries/groups of countries.

```{r init}
```
```{r,fig.cap="Per Capita GHG Emissions, 2019, Top Emittters, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

Considering GDP and GDP per capita refers to the capacity of acting on climate change, following the assumption that richer countries have more resources available to fight climate change. As Figure 3.12 shows, China had the highest GDP of all countries in 2019, with USD 22.49 trillion. Based on this, China would theoretically have to make the greatest contribution to reduce emissions. Absolute GDP, however, is limited in telling us about a country's actual capacity because it ignores population size. Therefore, considering GDP per capita might be more worthwhile. Here China only ranks 81st place in the world. Therefore, China’s responsibility is relatively low from the GDP per capita perspective. In comparison, the U.S. rank on place 11. Countries that are in the top 10 emitters are often relatively small countries deriving their wealth from natural resources. Hence, they have a high responsibility to mitigate climate change as they have the ability to pay for climate change mitigation measures. However, their absolute emissions are relatively small and thus an ambitious reduction might not make a huge difference for achieving climate targets. Thus, one should consider that these countries should specifically contribute by providing financial aid to mitigate emissions elsewhere.

```{r init}
```
```{r,fig.cap="Absolute GDP 2019, Countries with highest GDP, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

```{r init}
```
```{r,fig.cap="GDP per Capita 2019, Countries with highest GDP, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"
